Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Updated Model Descriptions

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

>>>>

- pct: The percentage of the vote or support that the candidate received in the poll (e.g., 51.0 for Kamala Harris, 48.0 for Donald Trump).
- numeric_grade: A numeric rating given to the pollster to indicate their quality or reliability (e.g., 3.0).
- sample_size: The total number of respondents participating in the poll (e.g., 2712).
- transparency_score:A score reflecting the pollster’s transparency about their methodology (e.g., 9.0). "A grade for how transparent a pollster is, calculated based on how much information it discloses about its polls and weighted by recency. The highest Transparency Score is 10."
- state: The U.S. state where the poll was conducted or focused, if applicable.
- end_date: The date the poll ended (e.g., 10/11/24).
- $\epsilon_i$: The error term for poll accounting for variability not explained by the predictors.
